---
title: "Reproducible Research: Peer Assessment 1"
output: html_document
keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading and preprocessing the data

```{r}
repdata <- read.csv("./activity.csv")
repdata_1 <- na.omit (repdata)
library(dplyr)
library(ggplot2)
```

## Total number of steps per day
```{r}
result_total <- aggregate(repdata_1$steps~repdata_1$date,FUN = sum)
colnames(result_total) <- c("date","steps")
```
Histogram of daily steps number
```{r}
hist(result_total$steps,col = "red", main = "Daily steps per day")
```

## Mean and median number of steps per day

```{r}
result_mean <-mean(result_total$steps)
result_median <-median(result_total$steps)
print(result_mean)
print(result_median)
```

## Time series plots and the Max of step and relative intervals
```{r}
result_avg <- aggregate(repdata_1$steps~repdata_1$interval,FUN = mean)
colnames(result_avg) <-c("interval","steps")
step_max <-max(result_avg$steps)
interval_max <- result_avg$interval[result_avg$steps==step_max]
with(result_avg,plot(interval,steps,type="l",main="Average steps of every 5minutes in a day"))
print(interval_max)
print(step_max)
```

## Input missing data and Filling in NAs with average steps of 5 minutes interval
```{r}
nrow(repdata[is.na(repdata$steps),])
```
Filling in NAs with average steps of 5-minutes interval
```{r}
repdata_na<-repdata[is.na(repdata$steps),]
repdata_mg <-merge(repdata_na,result_avg,by = "interval")
repdata_fil<-repdata_mg[,c(4,3,1)]
colnames(repdata_fil)<-c("steps","date","interval")
repdata_new<-rbind(repdata_1,repdata_fil)
```
## Calculate the mean of new dataset and Plot histogram.
```{r}
result_new <- aggregate(repdata_new$steps~repdata_new$date,FUN = sum)
colnames(result_new)<-c("date","steps")
mean(result_total$steps)
mean(result_new$steps)

hist(result_new$steps,col = "red",main = "Daily steps per day adjusted")
hist(result_total$steps,col = "blue",add = T)
legend("topright",c("Adjusted Data","NA excluded data"),fill=c("red","blue"))
```
New mean and median
```{r}
Newmean<-mean(result_new$steps)
Newmedian<-median(result_new$steps)
Newmean
Newmedian
```
## Differences between weekdays and weekends
```{r}
library(lattice)
library(plyr)
repdata_new$day<-weekdays(as.Date(repdata_new$date))
repdata_new$wkd<-ifelse(repdata_new$day %in% c("星期六", "星期日"), "Weekend", "Weekday")
repdata_newAVG<-ddply(repdata_new,.(interval,wkd),summarize,Avg=mean(steps))
```
Plot the line figure using average number versus interval.

```{r}
xyplot(Avg~interval|wkd,data=repdata_newAVG,type="l",layout=c(1,2),main="Average Steps per Interval",ylab="Average Number of Steps",xlab="Interval")
```

